Data Specialization for a Staged Lambda Calculus

### 2014-11-06 paper/splitting.tex
First attempt at masking.

\subsection {Stage \bbtwo\ Splitting}

@@

\subsection{Stage \bbone\ Splitting}

@@

Note that this result carries information at {\em both} stages: 
at stage~\bbone\ it carries the value 3, and at stage~\bbtwo\ it carries the code $\letin \yhat {\mathtt{7+5}} \yhat$. 
Therefore, to make the results of splitting match the the partial value above, we choose to split \bbone\ terms to create a resumer that reduces to the same value as the stage~\bbtwo\ carried by the partial value, and an $e1$ that not only performs the precomputation necessary for the resumer, but also generates values that match the stage~\bbone\ aspects of the partial value.

@@

To concretize what it means by ``match", we introduce two {\em masking} functions, $\masko{\cdot}$ and $\maskt{\cdot}$, that project from the residual table and partial value only the parts that are relevant at a particular stage.  These functions are shown in \ref{fig:valMask}. They operate by replacing all stage \bbone\
(resp., \bbtwo) components of a partial value by \texttt{()}.

@@

>>>>

\subsection {Splitting Stage \bbtwo\ Terms}

@@

\subsection{Splitting Stage \bbone\ Terms}

@@

Note that this result simultaneously represents information at {\em both} stages: 
a stage~\bbone\ value 3, and the stage~\bbtwo\ computation $\letin \yhat {\mathtt{7+5}} \yhat$. 
Therefore, to make the results of splitting match the the partial value above, we choose to split \bbone\ terms in \lang\ into a resumer that reduces to the same value as the stage~\bbtwo\ computation, and an $e1$ that not only performs the precomputation expected by the resumer, but also computes values that match the stage~\bbone\ aspects of the partial value.

@@

\subsubsection{Partial Value Masking}

To concretize the meaning of ``match", we introduce two {\em partial value masking} functions, $\masko{\cdot}$ and $\maskt{\cdot}$, that project from the residual table and partial value only the subterms that are relevant at a particular stage.  The masking functions are defined in \ref{fig:valMask}.

Since \texttt{next}'s only contain references to the residual table (computations that occur in stage~\bbtwo),
the primary operation of $\masko{\xi;v}$ is to replace all $\next$s in $v$ with \texttt{()}.   The result is a \langmono\ value with the same structure as $v$, but containing only its stage~\bbone\ information. Masking is more complex when $v$ is a function since the function's body itself may contain stage~\bbtwo\ subterms.  As a result, masking of functions depends on the general behavior of stage~\bbone\ splitting, described shortly.

While $\masko{\cdot}$ produces a value in \langmono,
$\maskt{\xi;v}$ produces a \emph{term} in \langmono\ that corresponds to the stage~\bbtwo\ computation represented by $[\xi;v]$.
Stage~\bbone\ information in $v$ is discarded by replacing base constants with \texttt{()}, replacing $\next~\hat{y}$ with $\hat{y}$, and eliminating all injection tags. (The sum type is at stage \bbone, so the tag is not relevant at stage \bbtwo.)
Last, $\maskt{\cdot}$ reifies $\xi$ around the modified $v$ to produce a term in \langmono. 
As with $\masko{\cdot}$, function masking by $\maskt{\cdot}$ depends on general term splitting.

% For functions $\lam xAe$, masking again splits its body $e\splitonesym [c,l.r]$,
% replaces it with the resumer, and uncurries, to yield $\lambda (x,l).r$.

%The only exception is for
%functions $\lam xAe$; such a value represents a computation, so masking splits
%its body as a computation, $e\splitonesym [c,l.r]$, and replaces it with its
%stage \bbone\ component, the combined result.

%They operate by replacing all stage \bbone\
%(resp., \bbtwo) components of a partial value by \texttt{()}.

@@

\subsubsection{Splitting}
